### 2024-03-15 tesis_Ashish/Chapter5/chapter5.tex
update 15 Mar 2024

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM_fit_1.png}
\caption[2022 PCC vdM Fit]{%                                                                                                                                              
  Rates and the resulting fitted double Gaussian scan curves as a function of the beam separation for a single bunch (BCID 282) as recorded by PCC for a vdM1 scan in the x (left) and y direction (right). Beam corrections have been applied to the raw data before the fit.
}
\label{fig:period_bound_50}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_sigma_vis_per_scan.png}
\caption[2022 PCC Visible Cross Section]{%                                                                                                                                                                               
  Visible cross section per scan where red line shows the average value. Red band depicts the RMS of the values.
}
\label{fig:period_bound_105}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all_2022_1.png}
\caption[Projection of Luminosity Ratio Profile]{%                                                                                                                                                                                           
 Distribution of the ratio of PCC/HFET luminosity evaluated per 50 lumi section blocks.
}
\label{fig:stabprof1_79}
\end{figure}

@@

The left plot in figure \ref{fig:stabprof2_2000} provides a comparison of the linearity of PCC luminosity in relation to HFET luminosity. A perfectly linear relationship would imply same luminosity measured by both the luminometers, suggesting an absence of non-linearity in the detector response. The plot on the right in \ref{fig:stabprof2_2000} shows the ratio of luminosity values obtained using the PCC method to those from the HFET luminometer. The values are plotted as a function of HFET luminosity. The goal of this graph is to examine potential changes in the detector's response across different luminosity levels. If the detector's response was perfectly linear, we do expect the ratio to remain constant across the range of HFET luminosity values. Deviations from a constant ratio indicate non-linearity in the detector response, thereby contributing to systematic uncertainties.

@@

\begin{figure}[H]
  \centering
  %\begin{subfigure}[b]{0.49\textwidth}
   % \includegraphics[width=\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_all_2022.png}
    %\caption{Image 1}                                                                                                                                                                           
  %\end{subfigure}
  %\hfill % or \hspace{5mm} for a specific horizontal space                                                                                                                            
  %\begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=0.7\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all_2022_1.png}
    %\caption{Image 2}                                                                                                                                                                           
  %\end{subfigure}
    \caption[2022 PCC linearity]{%Left: Linearity of PCC compared to HFET.
      Ratio of PCC/HFET luminosity plotted as a function of HFET luminosity to determine change in detector response over different luminosity levels. Slope is 0.00114 ub/Hz. % $ PCC and HFET iovtags used are pcc22v2 and hfet22v10.$
  }

@@

\begin{table}[H]
  \centering
  \caption{Systematic uncertainty in luminosity measurement (\%) \cite{pas_22}}
    \begin{tabular}{l|c}
        \textbf{Source} & \textbf{Uncertainty (\%)} \\
        \hline
        \multicolumn{2}{c}{\textbf{Calibration}} \\
        \hline
        Beam current & 0.3 \\
        Orbit drift & 0.3 \\
        Residual beam positions & 0.4 \\
        Beam-beam effects & 0.4 \\
        Length scale & 0.1 \\
        Factorization bias & 0.8 \\
        Scan-to-scan variation & 0.5 \\
        Bunch-to-bunch variation & 0.1 \\
        Cross-detector consistency & 0.4 \\
        \hline
        \multicolumn{2}{c}{\textbf{Integration}} \\
        \hline
        Afterglow corrections & 0.2 \\
        Cross-detector stability & 0.5 \\
        Cross-detector linearity & 0.5 \\
        \hline
        Calibration & 1.3 \\
        Integration & 0.8 \\
        \hline
        \textbf{Total} & 1.5 \\
    \end{tabular}
    \label{table:correction_uncertainties}
    %\caption{Systematic uncertainty in luminosity measurement (\%)}
\end{table}

>>>>

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2022_PCC_vdM_fit_new.png}
\caption[2022 PCC vdM Fit]{%                                                                                                                                              
  Rates and the resulting fitted double Gaussian scan curves as a function of the beam separation for a single bunch (BCID 282) as recorded by PCC for a vdM1 scan in the x (left) and y direction (right). Beam corrections have been applied to the raw data before the fit.
}
\label{fig:period_bound_50}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_PCC_sigmavis_per_scan_new.png}
\caption[2022 PCC Visible Cross Section]{%                                                                                                                                                                               
  Visible cross section per scan where red line shows the average value. Red band depicts the RMS of the values.
}
\label{fig:period_bound_105}
\end{figure}

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all_2022_1_new.png}
\caption[Projection of Luminosity Ratio Profile]{%                                                                                                                                                                                           
 Distribution of the ratio of PCC/HFET luminosity evaluated per 50 lumi section blocks.
}
\label{fig:stabprof1_79}
\end{figure}

@@

The left plot in figure \ref{fig:stabprof2_2000} provides a comparison of the linearity of PCC luminosity in relation to HFET luminosity. A perfectly linear relationship would imply same luminosity measured by both the luminometers, suggesting an absence of non-linearity in the detector response. The plot in Fig. \ref{fig:stabprof2_2000} shows the ratio of luminosity values obtained using the PCC method to those from the HFET luminometer. The values are plotted as a function of HFET luminosity. The goal of this graph is to examine potential changes in the detector's response across different luminosity levels. If the detector's response was perfectly linear, we do expect the ratio to remain constant across the range of HFET luminosity values. Deviations from a constant ratio indicate non-linearity in the detector response, thereby contributing to systematic uncertainties.

@@

\begin{figure}[H]
  \centering
  %\begin{subfigure}[b]{0.49\textwidth}
   % \includegraphics[width=\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_all_2022.png}
    %\caption{Image 1}                                                                                                                                                                           
  %\end{subfigure}
  %\hfill % or \hspace{5mm} for a specific horizontal space                                                                                                                            
  %\begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=0.7\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all_2022_1_new.png}
    %\caption{Image 2}                                                                                                                                                                           
  %\end{subfigure}
    \caption[2022 PCC linearity]{%Left: Linearity of PCC compared to HFET.
      Ratio of PCC/HFET luminosity plotted as a function of HFET luminosity to determine change in detector response over different luminosity levels. Slope is 0.00114 ub/Hz. % $ PCC and HFET iovtags used are pcc22v2 and hfet22v10.$
  }

@@

\begin{table}[H]
  \centering
  \caption{Systematic uncertainty in luminosity measurement (\%) \cite{pas_22}}
    \begin{tabular}{l|c}
        \textbf{Source} & \textbf{Uncertainty (\%)} \\
        \hline
        \multicolumn{2}{c}{\textbf{Calibration}} \\
        \hline
        Beam current & 0.3 \\
        Orbit drift & 0.3 \\
        Residual beam positions & 0.4 \\
        Beam-beam effects & 0.4 \\
        Length scale & 0.1 \\
        Factorization bias & 0.8 \\
        Scan-to-scan variation & 0.5 \\
        Bunch-to-bunch variation & 0.1 \\
        Cross-detector consistency & 0.4 \\
        \hline
        \multicolumn{2}{c}{\textbf{Integration}} \\
        \hline
        Afterglow corrections & 0.2 \\
        Cross-detector stability & 0.6 \\
        Cross-detector linearity & 0.5 \\
        \hline
        Calibration & 1.3 \\
        Integration & 0.8 \\
        \hline
        \textbf{Total} & 1.5 \\
    \end{tabular}
    \label{table:correction_uncertainties}
    %\caption{Systematic uncertainty in luminosity measurement (\%)}
\end{table}
